paper_replication

### 2021-12-14 paper_replication.Rmd
Update paper_replication.Rmd

---
title: "paper_replication"
output: pdf_document
---

>>>>

---
title: "paper_replication"
output: pdf_document
---
REPLICATION:
TODO: make sure all the counties match/are represented <- Jo
TODO: t tests for the demographic info for table 2 <- Toby
TODO: averages of averages vs. averages for table 2 
TODO: possibly email Alice asking about this county vs. state table 2 issue <- Jo 
TODO: change variable name bc it's awful <- Jo
TODO: write up <- Toby
TODO: find abortion data used by Brown et al. to compare in discussion <- Toby

EXTENSION:
TODO: use all counties we have data on instead of just those 18 states
TODO: rescore the high vs. low restriction variable to make it make more sense
TODO: add in rural vs urban, % college grad, more variables do a quick variable selection
TODO: repeat for mortality and fertility <- Jo look for this data
